Robust DPG stability II

### 2012-04-02 docs/NewBCRobustness_paper/paper.tex
committing rewrite (with notes in red for unfinished portions) of the paper
git-svn-id: https://svn.ices.utexas.edu/repos/camellia@416 36274a68-8941-4c93-80ef-affaed5139da

The main goal of this paper is to derive a test norm that \textit{does not induce boundary layers in the optimal test functions}, but still induces an energy norm \textit{that does not lose robustness as $\epsilon \rightarrow 0$}.  The first condition is satisfied by first decoupling norms on $\left(\tau,v\right)$ such that
\[
\left\|\left(\tau,v\right)\right\|_V = \|\tau\|_{H({\rm div},\Omega_h)} +  \|v\|_{H^1(\Omega_h)}.
\]
Ensuring that each term $\|\tau\|_{H({\rm div},\Omega_h)}$ and $ \|v\|_{H^1(\Omega_h)}$ is of the same order will allow for smooth solutions (under some assumptions on $\beta$).  
\textcolor{red}{Why are we allowed to have $\beta\cdot \grad v$ of order 1 while we have other terms of order $O({\rm Pe})$?  Why does this term not induce boundary layers?}

Showing the second condition on robustness is equivalent to showing the robust equivalence of the $L^2$ error of the solution in a norm on $U$ (that does not grow as $\epsilon\rightarrow 0$) times the error in the energy norm
\[
\left(\|u\| + \|\sigma\| + \|\widehat{u}\| + \|\widehat{f}_n\|\right) \lesssim  \left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_E \lesssim \left(\|u\| + \|\sigma\| + \|\widehat{u}\| + \|\widehat{f}_n\|\right)
\]
where $\lesssim$ denotes a bound by a constant that will not grow as $\epsilon \rightarrow 0$.  
%$\left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_U \lesssim \left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_E$.  
Our strategy for proving such a bound is broken down into three parts.

\subsection{Translate equivalence norms on $U$ to norms on $V$}

We begin with a given norm on $U$
\[
\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_U = C_1 \|u\| + C_2 \|\sigma\| + C_3 \|\widehat{u}\| + C_4 \|\widehat{f}_n\|.
\]
By \eqref{norm_duality}, the duality of test norm and energy norm, a norm of this form induces the test norm
\begin{align*}
\|\left(v,\tau\right)\|_{V,U} &= \sup_{\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\in U}\frac{b\left(\left(u,\sigma,\widehat{u},\widehat{f}_n\right),\left(\tau,v\right)\right)}{C_1\|u\| + C_2\|\sigma\| + C_3\epsilon\|\widehat{u}\|+ C_4\sqrt{\epsilon}\|\widehat{u}\|}\\
&= \sup_{\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\in U}\frac{\left(u,\div \tau - \beta \cdot \grad v\right) + \left(\sigma, \epsilon^{-1} \tau + \grad v\right) - \langle \left[\tau_n\right], \widehat{u} \rangle_{\Gamma_-\cup \Gamma_h^0} + \langle \widehat{f}_n, \left[v\right] \rangle_{\Gamma_+ \cup \Gamma_h^0}}{C_1\|u\| + C_2\|\sigma\| + C_3\epsilon\|\widehat{u}\|+ C_4\sqrt{\epsilon}\|\widehat{u}\|}\\
& \leq \frac{1}{C_1}\|g\| + \frac{1}{C_2}\|f\| + \frac{1}{C_3}\sup_{\widehat{u}\neq 0, \left.\widehat{u}\right|_{\Gamma_+} = 0} \frac{\langle [\tau\cdot n], \widehat{u}\rangle}{\|\widehat{u}\|} +\frac{1}{C_4}\sup_{\widehat{f}_n\neq 0, \left.\widehat{f}_n\right|_{\Gamma_-}=0}\frac{\langle \widehat{f}_n, [v]\rangle}{\|\widehat{f}\|}
\end{align*}
where $f$ and $g$ are defined as 
\begin{align*}
g &\coloneqq \div \tau - \beta \cdot \grad v\\
f &\coloneqq \epsilon^{-1}\tau + \grad v
\end{align*}
which, by definition of the boundary norms, gives the characterization of the induced test norm 
\[
\|\left(v,\tau\right)\|_{V,U} \leq \frac{1}{C_1}\|g\| + \frac{1}{C_2}\|f\| + \frac{1}{C_3}\|[\tau\cdot n]\| + \frac{1}{C_4}\|[v]\|
\]
\textcolor{red}{is this an equality? Is the inequality attainable, and thus attained in the supremum?} We can now use this relation to compare two different norms on $U$ by comparing their induced norms on $V$.  Additionally, showing a robust inequality between two norms on $U$ is similarly equivalent to showing the robust reverse inequality in the induced norms on $V$.

\subsection{Decomposition into analyzable components}

After reducing the problem of comparing norms on $U$ to comparing norms on $V$, we break the analysis of $\left(\tau,v\right) \in V$ into the analysis of subproblems.  Define the decomposition
\[
\left(v,\tau\right) = \left(v_0,\tau_0\right) + \left(v_1,\tau_1\right) + \left(v_2,\tau_2\right),
\]
where $\left(v_1,\tau_1\right)$ satisfies 
\begin{align*}
\epsilon^{-1}\tau_1 + \grad v_1 &= 0\\
\div \tau_1 - \beta\cdot \grad v_1 &=  \div \tau - \beta\cdot \grad v = g,
\end{align*} 
Likewise, we define $\left(v_2,\tau_2\right)$ as satisfying
\begin{align*}
\epsilon^{-1}\tau_2 + \grad v_2 &= \epsilon^{-1}\tau + \grad v = f\\
\div \tau_2 - \beta\cdot \grad v_2 &= 0
\end{align*}
We will additionally require both $\left(\tau_1,v_1\right)$ and $\left(\tau_2,v_2\right)$ to come from $H({\rm div}, \Omega)\times H^1(\Omega)$, and to satisfy boundary conditions
\begin{align*}
\tau_i\cdot n &= 0, \quad x \in \Gamma_-\\
v_i &= 0, \quad x \in \Gamma_+
\end{align*}
for $i = 1, 2$.  The selection of $H({\rm div}, \Omega)\times H^1(\Omega)$ conforming test functions satisfying the specific above boundary conditions removes the contribution of the jump terms over the skeleton $\Gamma_h$ in the bilinear form, allowing us to bound components of the induced test norm separately from each other.

@@

We have now decomposed any arbitrary test function $\left(\tau,v\right)$ into a single discontinuous portion and two conforming portions.  Showing robust equivalence of $\|\left(v,\tau\right)\|_V$ with another norm $\|\cdot \|_{?}$ on $V$ reduces to showing robust equivalence of each component 
\[
C_1\|\left(\tau,v\right)\|_{?} \lesssim \|\left(v_{0},\tau_{0}\right)\|_V, \|\left(v_{1},\tau_{1}\right)\|_V, \|\left(v_{2},\tau_{2}\right)\|_V \lesssim C_2\|\left(\tau,v\right)\|_{?}
\]
Bounding $\|\left(\tau_0,v_0\right)\|$ requires the use of techniques and decompositions first developed in \cite{analysisDPG} and adapted to convection-diffusion in \cite{DPGrobustness}.  However, due to the conforming nature of $\left(\tau_1,v_1\right)$ and $\left(\tau_2,v_2\right)$, the bound from above of test functions $\|\left(\tau_{1,2},v_{1,2}\right)\| \leq C\|g\|$ is reduced to proving classical error estimates for the adjoint equation
\begin{align*}
\epsilon^{-1}\tau + \grad v &= f\\
\div \tau - \beta\cdot \grad v &=  g,
\end{align*} 
for data $f, g\in L^2({\Omega_h})$ and boundary conditions $\left.\tau\cdot n\right|_{\Gamma_-} = 0$ and $\left.v\right|_{\Gamma_+} = 0$

\subsection{Deriving adjoint estimates}

@@

We introduce first the bounds derived; the proofs will be given later.  Under specific assumptions on $\beta$, we have the robust bounds
\begin{itemize}
\item For $f=0$ and $v \in H^1(\Omega_h)$, satisfying boundary conditions \eqref{bc_1} and \eqref{bc_2}
\begin{align*}
\|\beta \cdot \grad v \| &\lesssim \| g\| 
\end{align*}
\item For $v \in H^1(\Omega_h)$ and satisfying boundary conditions \eqref{bc_1} and \eqref{bc_2}, and for sufficiently small $\epsilon$
\begin{align*}
\epsilon \|\grad v\|^2 + \|v\|^2 &\lesssim \|g\|^2 + \epsilon \| f\|^2
\end{align*}
\item For $f=g=0$, 
\begin{align*}
\|\grad v\| = \frac{1}{\epsilon}\|\tau\| &\lesssim \frac{1}{\epsilon} \| [\tau\cdot n]\|_{\Gamma_h \setminus \Gamma_+} + \frac{1}{\sqrt{\epsilon}} \| [v]\|_{\Gamma_h^0 \cup \Gamma_+}
\end{align*}
\end{itemize}
Together, these estimates will be sufficient to complete the first step and demonstrate bounds on induced test norms for different scalings of norms on $U$.

\section{Actually proving things}

\subsubsection{Induced adjoint boundary conditions}

Demkowicz and Heuer proved in \cite{DPGrobustness} that for Dirichlet boundary conditions, robustness as $\epsilon \rightarrow 0$ is achieved by the test norm
\[
\|\left(\tau, v\right)\|_{V,w}^2 = \|v\| + \epsilon \|\grad v\| + \|\beta \cdot \grad v\|_{w+\epsilon} + \| \div \tau\|_{w+\epsilon} + \frac{1}{\epsilon}\|\tau\|_{w+\epsilon}
\]
where $\|\cdot \|_{w+\epsilon}$ is a weighted $L^2$ norm, where the weight $w \in (0,1)$ is required to vanish on $\Gamma_-$ and satisfy $\grad w = O(1)$.

The need for the weight is intuitively explained by the induced adjoint problem.  The bilinear form for the Dirichlet case is 
\[
b\left(\left(u,\sigma, \widehat{u}, \widehat{\sigma}_n\right), \left(\tau, v\right)\right) = \left(u,\div \tau - \beta \cdot \grad v\right) + \left(\sigma, \epsilon^{-1} \tau + \grad v\right) + \langle \widehat{f}_n, \left[v\right] \rangle
\]
We note that 
\begin{align*}
b\left(\left(u,\sigma, \widehat{u}, \widehat{\sigma}_n\right), \left(\tau, v\right)\right) &= \left(u,\div \tau - \beta \cdot \grad v\right) + \left(\sigma, \epsilon^{-1} \tau + \grad v\right) - \langle \left[\tau_n\right], \widehat{u} \rangle_{\Gamma_-\cup \Gamma_h^0} + \langle \widehat{f}_n, \left[v\right] \rangle_{\Gamma_+ \cup \Gamma_h^0} \\
&= \| u \|^2_{L^2}
\end{align*}
for the specific continuous test functions $\tau$ and $v$ satisfying
\begin{align*}
\div \tau - \beta \cdot \grad v &= u \\
\frac{1}{\epsilon}\tau + \grad v &= 0
\end{align*}
with boundary conditions
\begin{align}
\tau_n &= 0, \quad x\in \Gamma_-\cup \Gamma_0 \label{eq:adj_bc1}\\
v &= 0, \quad x\in \Gamma_+ \label{eq:adj_bc2}
\end{align}
Choosing a continuous conforming test function $v$ removes the contribution of the term $\langle \widehat{f}_n, \left[v\right] \rangle$ on the mesh skeleton, while the boundary conditions remove the contribution of boundary terms from the bilinear form.  Then, for this specific choice of $\left(\tau, v\right)$, 
\begin{align*}
\|u\|_{L^2}^2 &= b\left(\left(u,\sigma, \widehat{u}, \widehat{\sigma}_n\right), \left(\tau, v\right)\right) = \frac{b\left(\left(u,\sigma, \widehat{u}, \widehat{\sigma}_n\right), \left(\tau, v\right)\right)}{\|\left(\tau, v\right)\|_V}\|\left(\tau, v\right)\|_V \leq \|u\|_E \|\left(\tau, v\right)\|_V
\end{align*}
At minimum, we want $\|u\|_{L^2} \lesssim \|u\|_E$, which requires 
\[
\|\left(\tau, v\right)\|_V \lesssim \| u \|_{L^2}
\]
for any choice of $u \in L^2$ (dividing through by $\|u\|_{L^2}$ gives the desired result).  This can be considered a ``sanity check"; at the minimum, we at least want control over the behavior of the single field variable $u$.  However, we are unable to prove this in the case of Dirichlet boundary conditions. Consider the convection-diffusion problem in 1D

\textcolor{red}{add 1D issue with control over $\|v'\|$ here}

\subsection{Equivalence of energy and $U$ norms}

For this analysis, it will be necessary to assume certain conditions on $\beta$.  For each proof, we require $\beta \in C^2(\bar{\Omega})$ and $\beta, \div \beta = O(1)$.  Additionally, we will assume some or all of the following assumptions
\begin{align}
&\curl \beta = 0, \quad 0<C \leq \left | \beta\right |^2 + \frac{1}{2}\div \beta, \quad C = O(1) \label{a_req}\\
&\grad \beta + \grad \beta ^T - \div \beta I = O(1) \label{b_req}\\
&\div \beta = 0 \label{c_req}
\end{align}

The primary result of this paper is that, if conditions \ref{a_req},\ref{b_req}, and \ref{c_req} are all satisfied, the DPG method provides robust control over the $L^2$ error in $u$ and $\sigma$
\[
\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)-\left(u_h,\sigma_h,\widehat{u}_h,\widehat{f}_{n,h}\right)\right\|_{U_1} \lesssim \inf_{w\in U_h}\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)-w_h \right\|_{E}
\]
using the test norm
\[
\|\left(\tau, v\right)\|_{V}^2 = \|v\|^2 + \epsilon \|\grad v\|^2 + \|\beta \cdot \grad v\|^2 + \| \div \tau\|^2 + \frac{1}{\epsilon}\|\tau\|^2
\]
where $\|\cdot \|_{U_1}$ is defined as
\[
\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_{U_1}^2 \coloneqq \|u\|^2 + \|\sigma\|^2 + \epsilon^2\|\widehat{u}\|^2+\epsilon \|\widehat{f}_n\|^2.
\]
%\textcolor{red}{should be explained here}.

A second, weaker result is an upper bound on the energy norm
\[
\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)-\left(u_h,\sigma_h,\widehat{u}_h,\widehat{f}_{n,h}\right)\right\|_{E} \lesssim \inf_{w\in U_h}\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)-w_h\right\|_{U_2}
\]
where $\|\cdot \|_{U_2}$ is defined as
\[
\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_{U_2}^2 \coloneqq \|u\|^2 + \frac{1}{\sqrt{\epsilon}}\left(\|\sigma\|^2 + \|\widehat{u}\|^2+ \|\widehat{f}_n\|^2\right).
\]
The upper bound on the energy norm appears to depend on $\epsilon^{-1/2}$, implying that for very small $\epsilon$, the $L^2$ error may be much smaller than the energy error. However, numerical experiments demonstrate much better results, and suggest that, at least for our examples, $\|u-u_h\|_E \sim \|u-u_h\|_{U}$, implying that the induced energy norm is equivalent to the canonical norms we have chosen on the group variable $\left(u,\sigma,\widehat{u},\widehat{f}_n\right)$.

The proof proceeds in two steps; the bound from below is proven by providing stability estimates for the adjoint problem, while the bound from above of the energy norm is proven separately.

\subsubsection{Bound from below}
\textcolor{red}{introduce the three lemmas}
With these three lemmas, we can prove the robust bound of both field variables and fluxes by the energy error.  In doing so, we take advantage of the fact that, for any choice of energy norm, the test norm $\|v\|_V$ inducing it can be recovered via duality
\begin{align}
\| v \|_V = \sup_{u \in U\setminus \{0\}} \frac{b\left(u,v\right)}{\left\| u \right\|_E} \label{norm_duality}
\end{align}
The proof for this is identical to proving $\|u\|_E = \|u\|_U$ for the choice of the optimal test norm.

@@

Lemma \ref{lemma_grad} provides
\[
\epsilon \|\grad v\|^2 + \|v\|^2 \lesssim  \epsilon \| f\|^2 \leq \|f\|^2
\]
We have $\epsilon^{-1}\tau = f - \grad v$, so $\epsilon^{-1} \|\tau\| \lesssim \|f\| + \|\grad v\|$. Lemma 1 implies $\|\grad v\|^2  \lesssim  \| f\|^2$, so for $\epsilon \leq 1$, we control $\epsilon^{-1/2}\|\tau\| \leq \epsilon^{-1}\|\tau\| \lesssim \|f\|$.  The remaining terms can be bounded by noting that, with $g = 0$, $\|\div \tau_2\| = \|\beta\cdot \grad v_2\| \lesssim \|\grad v_2\| \lesssim \|f\| $.
\end{itemize}
\end{proof}

\subsubsection{Bound from above}

@@

We reduce the adjoint problem to the scalar second order equation
\begin{equation}
- \epsilon \Delta v - \beta \cdot \grad v = g - \epsilon \div f \label{adjoint}
\end{equation}
with boundary conditions
\begin{align}
%\tau \cdot n = 
- \epsilon \grad v \cdot n &=f\cdot n, \quad x\in \Gamma_- \label{bc_1}\\ 
v &= 0, \quad x\in \Gamma_+ \label{bc_2}
\end{align}
and treat the cases $f=0$, $g=0$ separately.  %The above boundary conditions simplify to \eqref{eq:adj_bc1} and \eqref{eq:adj_bc2} when requesting $L^2$ robustness in $u$ ($f=0$); these more general boundary conditions are necessary for bounds involving $f \neq 0$. 
\textcolor{red}{motivate boundary conditions here}

@@

>>>>

The main goal of this paper is to derive a test norm that \textit{does not induce boundary layers in the optimal test functions}, but still induces an energy norm \textit{that does not lose robustness as $\epsilon \rightarrow 0$}.  The first condition is satisfied by first decoupling norms on $\left(\tau,v\right)$ such that
\[
\left\|\left(\tau,v\right)\right\|_V = \|\tau\|_{H({\rm div},\Omega_h)} +  \|v\|_{H^1(\Omega_h)}.
\]
where $\|\tau\|_{H({\rm div},\Omega_h)}$ and $ \|v\|_{H^1(\Omega_h)}$ are both constructed as the sum of norm and seminorms on each respective space.  Ensuring that each seminorm/normed term is of the same order will allow for smooth solutions (under some assumptions on $\beta$).  The avoidance of boundary layers in the test norm will be described in more detail in the section detailing numerical experiments.  
\textcolor{red}{Why are we allowed to have $\beta\cdot \grad v$ of order 1 while we have other terms of order $O({\rm Pe})$?  Why does this term not induce boundary layers?}

Showing the second condition on robustness is equivalent to showing the robust boundedness of the energy error from above and below by norms on $U$ 
\[
\left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_{U,1} \lesssim  \left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_E \lesssim \left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_{U,2}
\]
where $\lesssim$ denotes a bound by a constant that will not grow as $\epsilon \rightarrow 0$.  
%$\left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_U \lesssim \left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_E$.  
Our strategy for proving such a bound is broken down into three parts.

\subsection{Equate relations between norms on $U$ and norms on $V$}
\label{sec:strategy1}
We begin with a given norm on $U$
\[
\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_U = C_1 \|u\| + C_2 \|\sigma\| + C_3 \|\widehat{u}\| + C_4 \|\widehat{f}_n\|.
\]
By \eqref{norm_duality}, the duality of test norm and energy norm, a norm of this form induces the test norm
\begin{align*}
\|\left(v,\tau\right)\|_{V,U} &= \sup_{\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\in U}\frac{b\left(\left(u,\sigma,\widehat{u},\widehat{f}_n\right),\left(\tau,v\right)\right)}{C_1\|u\| + C_2\|\sigma\| + C_3\epsilon\|\widehat{u}\|+ C_4\sqrt{\epsilon}\|\widehat{u}\|}\\
&= \sup_{\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\in U}\frac{\left(u,\div \tau - \beta \cdot \grad v\right) + \left(\sigma, \epsilon^{-1} \tau + \grad v\right) - \langle \left[\tau_n\right], \widehat{u} \rangle_{\Gamma_-\cup \Gamma_h^0} + \langle \widehat{f}_n, \left[v\right] \rangle_{\Gamma_+ \cup \Gamma_h^0}}{C_1\|u\| + C_2\|\sigma\| + C_3\epsilon\|\widehat{u}\|+ C_4\sqrt{\epsilon}\|\widehat{u}\|}\\
& \leq \frac{1}{C_1}\|g\| + \frac{1}{C_2}\|f\| + \frac{1}{C_3}\sup_{\widehat{u}\neq 0, \left.\widehat{u}\right|_{\Gamma_+} = 0} \frac{\langle [\tau\cdot n], \widehat{u}\rangle}{\|\widehat{u}\|} +\frac{1}{C_4}\sup_{\widehat{f}_n\neq 0, \left.\widehat{f}_n\right|_{\Gamma_-}=0}\frac{\langle \widehat{f}_n, [v]\rangle}{\|\widehat{f}\|}
\end{align*}
where $f$ and $g$ are defined as 
\begin{align*}
g &\coloneqq \div \tau - \beta \cdot \grad v\\
f &\coloneqq \epsilon^{-1}\tau + \grad v
\end{align*}
which, by definition of the boundary norms, gives the characterization of the induced test norm 
\[
\|\left(v,\tau\right)\|_{V,U} \leq \frac{1}{C_1}\|g\| + \frac{1}{C_2}\|f\| + \frac{1}{C_3}\|[\tau\cdot n]\| + \frac{1}{C_4}\|[v]\|
\]
\textcolor{red}{is this an equality? Is the inequality attainable, and thus attained in the supremum?} We can now use this relation to compare two different norms on $U$ by comparing their induced norms on $V$.  Additionally, showing a robust inequality between two norms on $U$ is similarly equivalent to showing the robust reverse inequality in the induced norms on $V$.

\subsection{Decomposition into analyzable components}
\label{sec:strategy2}

After reducing the problem of comparing norms on $U$ to comparing norms on $V$, we break the analysis of $\left(\tau,v\right) \in V$ into the analysis of subproblems.  Define the decomposition
\[
\left(v,\tau\right) = \left(v_0,\tau_0\right) + \left(v_1,\tau_1\right) + \left(v_2,\tau_2\right),
\]
where $\left(v_1,\tau_1\right)$ satisfies 
\begin{align*}
\epsilon^{-1}\tau_1 + \grad v_1 &= 0\\
\div \tau_1 - \beta\cdot \grad v_1 &=  \div \tau - \beta\cdot \grad v = g,
\end{align*} 
Likewise, we define $\left(v_2,\tau_2\right)$ as satisfying
\begin{align*}
\epsilon^{-1}\tau_2 + \grad v_2 &= \epsilon^{-1}\tau + \grad v = f\\
\div \tau_2 - \beta\cdot \grad v_2 &= 0
\end{align*}
We will additionally require both $\left(\tau_1,v_1\right)$ and $\left(\tau_2,v_2\right)$ to come from $H({\rm div}, \Omega)\times H^1(\Omega)$, and to satisfy boundary conditions
\begin{align}
\tau_i\cdot n &= 0, \quad x \in \Gamma_- \label{bc_1}\\
v_i &= 0, \quad x \in \Gamma_+ \label{bc_2}
\end{align}
for $i = 1, 2$.  The selection of $H({\rm div}, \Omega)\times H^1(\Omega)$ conforming test functions satisfying the specific above boundary conditions removes the contribution of the jump terms over the skeleton $\Gamma_h$ in the bilinear form, allowing us to bound components of the induced test norm separately from each other.

@@

We have now decomposed any arbitrary test function $\left(\tau,v\right)$ into a single discontinuous portion and two conforming portions.  Showing the robust bound of $\|\left(v,\tau\right)\|_V$ from above and below (by norms $\|\cdot \|_{V,1}$ and $\|\cdot \|_{V,2}$ on $V$, respectively) reduces to showing the robust bound of each component 
\[
\|\left(\tau,v\right)\|_{V,1} \lesssim \|\left(v_{0},\tau_{0}\right)\|_V, \|\left(v_{1},\tau_{1}\right)\|_V, \|\left(v_{2},\tau_{2}\right)\|_V \lesssim \|\left(\tau,v\right)\|_{V,2}
\]
Bounding $\|\left(\tau_0,v_0\right)\|$ requires the use of techniques and decompositions first developed in \cite{analysisDPG} and adapted to convection-diffusion in \cite{DPGrobustness}.  However, due to the conforming nature of $\left(\tau_1,v_1\right)$ and $\left(\tau_2,v_2\right)$, the bound from above of test functions $\|\left(v_{1},\tau_{1}\right)\|_V, \|\left(v_{2},\tau_{2}\right)\|_V \lesssim \|g\|$ is reduced to proving classical error estimates for the adjoint equations
\begin{align}
\epsilon^{-1}\tau + \grad v &= f \label{adjoint1}\\
\div \tau - \beta\cdot \grad v &=  g, \label{adjoint2}
\end{align} 
for any choice of data $f, g\in L^2({\Omega_h})$ and boundary conditions $\left.\tau\cdot n\right|_{\Gamma_-} = 0$ and $\left.v\right|_{\Gamma_+} = 0$

\subsection{Deriving adjoint estimates}
\label{sec:strategy3}

@@

We introduce first the bounds derived; the proofs will be given later. For this analysis, it will be necessary to assume certain technical conditions on $\beta$.  For each proof, we require $\beta \in C^2(\bar{\Omega})$ and $\beta, \div \beta = O(1)$.  Additionally, we will assume some or all of the following assumptions hold
\begin{align}
&\curl \beta = 0, \quad 0<C \leq \left | \beta\right |^2 + \frac{1}{2}\div \beta, \quad C = O(1) \label{a_req}\\
&\grad \beta + \grad \beta ^T - \div \beta I = O(1) \label{b_req}\\
&\div \beta = 0 \label{c_req}
\end{align}
Additionally, as these results are primarily interested in stability and robustness for $\epsilon \ll 1$, we require $\epsilon$ sufficiently small in Lemma \ref{lemma_grad}.

Under proper assumptions on $\beta$, we have the robust bounds
\begin{itemize}
\item \textbf{Lemma \ref{lemma_stream}}: For $\beta$ satisfying \eqref{a_req} and \eqref{b_req}, $f=0$ and $v \in H^1(\Omega_h)$, satisfying boundary conditions \eqref{bc_1} and \eqref{bc_2}
\begin{align*}
\|\beta \cdot \grad v \| &\lesssim \| g\| 
\end{align*}
Similarly, from $\div \tau - \beta\cdot \grad v = g$, we get $\|\div \tau\| \lesssim \|g\|$ as well.  
\item \textbf{Lemma \ref{lemma_grad}}: For $\beta$ satisfying \eqref{a_req}, and $v \in H^1(\Omega_h)$ satisfying boundary conditions \eqref{bc_1} and \eqref{bc_2}, and for sufficiently small $\epsilon$
\begin{align*}
\epsilon \|\grad v\|^2 + \|v\|^2 &\lesssim \|g\|^2 + \epsilon \| f\|^2
\end{align*}
\item \textbf{Lemma \ref{lemma_boundary}}: For $\beta$ satisfying \eqref{a_req}, \eqref{c_req}, and $f=g=0$, 
\begin{align*}
\|\grad v\| = \frac{1}{\epsilon}\|\tau\| &\lesssim \frac{1}{\epsilon} \| [\tau\cdot n]\|_{\Gamma_h \setminus \Gamma_+} + \frac{1}{\sqrt{\epsilon}} \| [v]\|_{\Gamma_h^0 \cup \Gamma_+}
\end{align*}
\end{itemize}
Together, these estimates will be sufficient to complete the first step and demonstrate bounds on induced test norms for different scalings of norms on $U$.

\section{Relations between energy and $U$ norms}

The primary result of this paper is that, if $\beta$ satisfies \ref{a_req},\ref{b_req}, and \ref{c_req}, the DPG method provides robust control over the $L^2$ error in $u$ and $\sigma$
\[
\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)-\left(u_h,\sigma_h,\widehat{u}_h,\widehat{f}_{n,h}\right)\right\|_{U_1} \lesssim \inf_{w\in U_h}\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)-w_h \right\|_{E}
\]
using the test norm
\[
\|\left(\tau, v\right)\|_{V}^2 = \|v\|^2 + \epsilon \|\grad v\|^2 + \|\beta \cdot \grad v\|^2 + \| \div \tau\|^2 + \frac{1}{\epsilon}\|\tau\|^2
\]
where $\|\cdot \|_{U_1}$ is defined as
\[
\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_{U_1} \coloneqq \|u\| + \|\sigma\| + \epsilon\|\widehat{u}\|+\sqrt{\epsilon} \|\widehat{f}_n\|.
\]
%\textcolor{red}{should be explained here}.

A second, weaker result is an upper bound on the energy norm
\[
\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)-\left(u_h,\sigma_h,\widehat{u}_h,\widehat{f}_{n,h}\right)\right\|_{E} \lesssim \inf_{w\in U_h}\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)-w_h\right\|_{U_2}
\]
where $\|\cdot \|_{U_2}$ is defined as
\[
\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_{U_2}^2 \coloneqq \|u\|^2 + \frac{1}{\sqrt{\epsilon}}\left(\|\sigma\|^2 + \|\widehat{u}\|^2+ \|\widehat{f}_n\|^2\right).
\]
While the upper bound is robust, we have derived such a bound only by explicitly accounting for a factor of $\epsilon^{-1/2}$ in the bounding norm $\|\cdot \|_{U_2}$.  This implying that for very small $\epsilon$, the $L^2$ error may be much smaller than the energy error.  However, \textcolor{red}{explain why this is OK practically.}
Additionally, numerical experiments demonstrate much better results, and suggest that, at least for our examples, $\|u-u_h\|_E \sim \|u-u_h\|_{U}$, implying that the induced energy norm is equivalent to the canonical norms we have chosen on the group variable $\left(u,\sigma,\widehat{u},\widehat{f}_n\right)$.

\subsection{Bound from below}

We begin by using the strategy outlined in sections~\ref{sec:strategy1}, ~\ref{sec:strategy2}, and ~\ref{sec:strategy3} to prove the robust bound of the $L^2$ error in the field variables by the energy error.

@@

Lemma \ref{lemma_grad} provides
\[
\epsilon \|\grad v\|^2 + \|v\|^2 \lesssim  \epsilon \| f\|^2 \leq \|f\|^2
\]
We have $\epsilon^{-1}\tau = f - \grad v$, so $\epsilon^{-1} \|\tau\| \lesssim \|f\| + \|\grad v\|$. Lemma~\ref{lemma_grad} implies $\|\grad v\|^2  \lesssim  \| f\|^2$, so for $\epsilon \leq 1$, we control $\epsilon^{-1/2}\|\tau\| \leq \epsilon^{-1}\|\tau\| \lesssim \|f\|$.  The remaining terms can be bounded by noting that, with $g = 0$, $\|\div \tau_2\| = \|\beta\cdot \grad v_2\| \lesssim \|\grad v_2\| \lesssim \|f\| $.
\end{itemize}

With these characterizations, we can conclude that $C_1 = C_2 = 1$, $C_3 = \epsilon$, and $C_4 = \epsilon^{1/2}$.  
\end{proof}

\subsection{Bound from above}

@@

We reduce the adjoint problem to the scalar second order equation
\begin{equation}
- \epsilon \Delta v - \beta \cdot \grad v = g - \epsilon \div f \label{adjoint}
\end{equation}
with boundary conditions
\begin{align}
%\tau \cdot n = 
- \epsilon \grad v \cdot n &=f\cdot n, \quad x\in \Gamma_- \label{reducedbc_1}\\ 
v &= 0, \quad x\in \Gamma_+ \label{reducedbc_2}
\end{align}
and treat the cases $f=0$, $g=0$ separately.  The above boundary conditions are the reduced form of boundary conditions \eqref{bc_1} and \eqref{bc_2}.

@@

\subsection{Comparison of boundary conditions}

It's worth addressing the effect of boundary conditions on stability.  Specifically, a test norm that provides stability for one set of boundary conditions may perform poorly for another set of boundary conditions.  Demkowicz and Heuer proved in \cite{DPGrobustness} that for Dirichlet boundary conditions, robustness as $\epsilon \rightarrow 0$ is achieved by the test norm
\[
\|\left(\tau, v\right)\|_{V,w}^2 = \|v\| + \epsilon \|\grad v\| + \|\beta \cdot \grad v\|_{w+\epsilon} + \| \div \tau\|_{w+\epsilon} + \frac{1}{\epsilon}\|\tau\|_{w+\epsilon}
\]
where $\|\cdot \|_{w+\epsilon}$ is a weighted $L^2$ norm, where the weight $w \in (0,1)$ is required to vanish on $\Gamma_-$ and satisfy $\grad w = O(1)$.
